---
title: "CELF-5 Assessment Report"
subtitle: "Clinical Evaluation of Language Fundamentals — Fifth Edition"
output:
  word_document:
    toc: true
    toc_depth: 3
params:
  assessment_id: NA
  student_name: NA
  student_sex: NA
  age_years: NA
  age_months: NA
  age_days: NA
  age_group: NA
  assessment_date: NA
  examiner_name: NA
  scaled_scores: NA
  indices: NA
  raw_scores: NA
  overall_en: NA
  overall_zh: NA
---

```{r setup, include=FALSE}
library(dplyr)
library(flextable)
library(officedown)
library(tibble)
```

```{r student-info, echo=FALSE, results="asis"}
ss  <- params$scaled_scores
idx <- params$indices
ag  <- params$age_group

# Build subtest table
df_ss <- if (is.data.frame(ss) && nrow(ss) > 0) {
  ss %>%
    mutate(
      Range = case_when(
        is.na(scaled_score)              ~ "No Score",
        scaled_score >= 13              ~ "Above Average",
        scaled_score >= 8               ~ "Average",
        scaled_score >= 7               ~ "Borderline",
        scaled_score >= 5               ~ "Below Average",
        TRUE                            ~ "Very Low"
      ),
      Interpretation = case_when(
        is.na(scaled_score)             ~ "No score available.",
        scaled_score >= 13              ~ "Performance significantly above age-level expectations; strong competency indicated.",
        scaled_score >= 8               ~ "Performance within the expected range; no significant difficulty identified.",
        scaled_score >= 7               ~ "Performance slightly below expected range; mild difficulty possible; monitoring recommended.",
        scaled_score >= 5               ~ "Performance below expected range; language disorder likely; further assessment warranted.",
        TRUE                            ~ "Performance significantly below expected range; language disorder strongly indicated; immediate intervention recommended."
      )
    )
} else {
  tibble(subtest = character(), raw_score = integer(), scaled_score = integer(), Range = character(), Interpretation = character())
}

# Build composite table
df_idx <- if (!is.null(idx) && length(idx) > 0) {
  comps <- c("CLS", "RLI", "ELI", "LCI")
  if (ag %in% c("5:0-5:5","5:6-5:11","6:0-6:5","6:6-6:11","7:0-7:11","8:0-8:11")) {
    comps <- c(comps, "LSI")
  } else {
    comps <- c(comps, "LMI")
  }
  idx_df <- tibble(
    Index = comps,
    Score = sapply(comps, function(c) {
      s <- idx[[c]]
      if (is.null(s) || is.na(s)) NA_real_ else s
    }),
    Percentile = sapply(comps, function(c) {
      p <- idx[[paste0(c, "_pct")]]
      if (is.null(p) || is.na(p)) NA_real_ else p
    })
  ) %>%
    mutate(
      Interpretation = case_when(
        is.na(Score)                    ~ "No score available.",
        Score >= 130                    ~ "Very Superior — Exceptional language ability well above age-level expectations.",
        Score >= 120                    ~ "Superior — Well above average; strong language skills.",
        Score >= 110                    ~ "High Average — Above average; within normal limits.",
        Score >= 90                     ~ "Average — Within the average range; consistent with age-level expectations.",
        Score >= 80                     ~ "Low Average — Slightly below average; student may benefit from targeted language support.",
        Score >= 70                     ~ "Borderline — Significantly below average; language disorder suggested; intervention strongly recommended.",
        TRUE                            ~ "Extremely Low — Far below average; significant language disorder requiring immediate intervention."
      )
    )
  idx_df
} else {
  tibble(Index = character(), Score = double(), Percentile = double(), Interpretation = character())
}
```

---

# Student Information

```{r student-table, echo=FALSE, results="asis"}
df_info <- tibble(
  `Item` = c("Name", "Sex", "Age", "Grade / Year", "Examiner", "Assessment Date", "Age Group"),
  `Information` = c(
    params$student_name,
    if (params$student_sex == "F") "Female" else "Male",
    sprintf("%d years %d months", params$age_years, params$age_months),
    "—",
    params$examiner_name %||% "—",
    params$assessment_date,
    params$age_group
  )
)
flextable(df_info) |> autofit() |> bold(part = "header")
```

---

# Overall Assessment

**Summary:**

`r params$overall_en`

---

# Subtest Scaled Scores

> Scaled Scores: Mean = 10, SD = 3. Range: 1–19. Scores of 8–12 are within the average range. Scores below 7 suggest the presence of difficulty.

```{r subtest-table, echo=FALSE, results="asis"}
if (nrow(df_ss) > 0) {
  ft <- flextable(df_ss %>% select(`Subtest` = subtest, `Raw Score` = raw_score,
                                   `Scaled Score` = scaled_score, Range, Interpretation))
  ft <- autofit(ft)
  ft <- bold(ft, part = "header")
  ft
} else {
  cat("\nNo subtest data available.\n")
}
```

---

# Composite Scores

> Composite Scores: Mean = 100, SD = 15. Scores of 90–110 are within the average range.

```{r composite-table, echo=FALSE, results="asis"}
if (nrow(df_idx) > 0) {
  df_idx_disp <- df_idx %>%
    mutate(
      `Standard Score` = ifelse(is.na(Score), "—", as.character(round(Score, 0))),
      `Percentile Rank` = ifelse(is.na(Percentile), "—", sprintf("%.1f", Percentile))
    ) %>%
    select(`Composite Score` = Index, `Standard Score`, `Percentile Rank`, Interpretation)
  ft2 <- flextable(df_idx_disp)
  ft2 <- autofit(ft2)
  ft2 <- bold(ft2, part = "header")
  ft2
} else {
  cat("\nNo composite score data available.\n")
}
```

---

# Recommendations

1. **Further Diagnostic Assessment:** Students whose language abilities fall below the average range are advised to undergo a more comprehensive diagnostic language assessment to determine the nature and severity of any language disorder.

2. **Parent/Guardian Communication:** It is recommended that assessment results be communicated to the student's parent or guardian, and that appropriate support be provided within the school setting.

3. **Language Intervention:** If a language disorder is identified, referral to a speech-language pathologist for detailed assessment and the development of an individualized intervention plan is strongly recommended.

4. **Reassessment:** A follow-up reassessment is recommended in 6 months to monitor progress and evaluate the effectiveness of any interventions provided.

---

# Appendix: Subtest Descriptions

| Abbrev. | Subtest Name | Skill Assessed |
|---------|-------------|----------------|
| SC | Sentence Comprehension | Ability to understand spoken sentences of varying syntactic complexity |
| LC | Linguistic Concepts | Ability to understand basic linguistic concepts presented orally |
| WS | Word Structure | Knowledge of morphological word-structure rules |
| WC | Word Classes | Ability to identify semantic relationships between words |
| FD | Following Directions | Ability to follow multi-step oral directions |
| FS | Formulated Sentences | Ability to formulate complete, correct sentences using target vocabulary |
| RS | Recalling Sentences | Ability to recall and accurately reproduce sentences |
| USP | Understanding Spoken Paragraphs | Ability to understand main ideas in spoken paragraphs |
| PP | Pragmatics Profile | Pragmatic language skills as observed across situations |
| WD | Word Definitions | Ability to define words by describing semantic features |
| SA | Sentence Assembly | Ability to construct grammatically well-formed sentences |
| SR | Semantic Relationships | Ability to interpret sentences involving semantic relationships |
| RC | Reading Comprehension | Ability to understand written passages |
| SW | Structured Writing | Ability to produce organized narrative writing |

---

*© 2013 NCS Pearson, Inc. All rights reserved. CELF-5 and its components may not be reproduced without written permission from Pearson.*

*Generated by CELF-5 Shiny Assessment System — `r Sys.Date()`*
